10th International Satisfiability Modulo Theories Competition (SMT-COMP 2015): Rules and Procedures

### 2015-06-07 rules/rules15.tex
(exit) command optional.

The benchmark script is in the concrete syntax of the SMT-LIB format,
version~2.0, though with a restricted set of commands.  A benchmark
script is a text file containing a sequence of SMT-LIB~v2 commands in
which:
%
\begin{enumerate}
\item In the main track, there may be a (single) \akey{set-option
  :print-success ...} command.  Note that {\tt success} outputs are
  ignored by the post-processor used by the
  competition.\footnote{SMT-LIB~2.0 requires that a solver produce a
    \texttt{success} answer after each \akey{set-logic},
    \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
    (among others), unless the option \akey{:print-success} is set to
    false.  Ignoring the \texttt{success} outputs allows for
    submitting fully SMT-LIB~2.0 compliant solvers without the need
    for a wrapper script, while still allowing entrants of previous
    competitions to run without changes.}
\item In the application track, the \akey{:print-success} option may
  not be disabled; the application track executor will send an initial
  $\akey{set-option :print-success true}$ command to the solver.
\item The (single) $\akey{set-logic}$ command setting the benchmark's
  logic is the first command after any $\akey{set-option}$ commands.
\item The script next optionally contains (any number of)
  $\akey{set-info}$ commands, which may be ignored by the
  solver. Benchmarks will likely have some of the following
  \akey{set-info} commands: \akey{(set-info :smt-lib-version 2.0)},
  \akey{(set-info :category ...)}, \akey{(set-info :source ...)}, and
  \akey{(set-info :status ...)}.
\item In the main track, there is exactly one $\akey{check-sat}$
  command, following possibly several $\akey{assert}$ commands.
\item In the application track, there are one or more \akey{check-sat}
  commands, each preceded by one or more \akey{assert} commands; there
  may also be zero or more \akey{push 1} commands, and zero or more
  \akey{pop 1} commands, consistent with the uses of those commands in
  the SMT-LIB standard. Each \akey{check-sat} command may be preceded
  by a \akey{set-info :status} command that indicates the expected
  result of the \akey{check-sat} command.
\item The $\akey{exit}$ command is the last command.
\item The formulas in the script belong to the benchmark's logic, with
  any free symbols declared in the script.
\item All sorts declared with a $\akey{declare-sort}$ command must
  have zero arity.
\item Application track scripts may have $\akey{define-sort}$
  commands.
\item No other commands besides the ones just mentioned may be used.
\item Named formulas are not used in benchmark scripts.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Documents''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.

>>>>

The benchmark script is in the concrete syntax of the SMT-LIB format,
version~2.0, though with a restricted set of commands.  A benchmark
script is a text file containing a sequence of SMT-LIB~v2 commands in
which:
%
\begin{enumerate}
\item In the main track, there may be a (single) \akey{set-option
  :print-success ...} command.  Note that {\tt success} outputs are
  ignored by the post-processor used by the
  competition.\footnote{SMT-LIB~2.0 requires that a solver produce a
    \texttt{success} answer after each \akey{set-logic},
    \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
    (among others), unless the option \akey{:print-success} is set to
    false.  Ignoring the \texttt{success} outputs allows for
    submitting fully SMT-LIB~2.0 compliant solvers without the need
    for a wrapper script, while still allowing entrants of previous
    competitions to run without changes.}
\item In the application track, the \akey{:print-success} option may
  not be disabled; the application track executor will send an initial
  $\akey{set-option :print-success true}$ command to the solver.
\item The (single) $\akey{set-logic}$ command setting the benchmark's
  logic is the first command after any $\akey{set-option}$ commands.
\item The script next optionally contains (any number of)
  $\akey{set-info}$ commands, which may be ignored by the
  solver. Benchmarks will likely have some of the following
  \akey{set-info} commands: \akey{(set-info :smt-lib-version 2.0)},
  \akey{(set-info :category ...)}, \akey{(set-info :source ...)}, and
  \akey{(set-info :status ...)}.
\item In the main track, there is exactly one $\akey{check-sat}$
  command, following possibly several $\akey{assert}$ commands.
\item In the application track, there are one or more \akey{check-sat}
  commands, each preceded by one or more \akey{assert} commands.
  There may also be zero or more \akey{push 1} commands, and zero or
  more \akey{pop 1} commands, consistent with the uses of those
  commands in the SMT-LIB standard. Each \akey{check-sat} command may
  be preceded by a \akey{set-info :status} command that indicates the
  expected result of the \akey{check-sat} command.
\item Optionally, the script may contain an $\akey{exit}$ command as
  its last command.
\item The formulas in the script belong to the benchmark's logic, with
  any free symbols declared in the script.
\item All sorts declared with a $\akey{declare-sort}$ command must
  have zero arity.
\item Application track scripts may have $\akey{define-sort}$
  commands.
\item No other commands besides the ones just mentioned may be used.
\item Named formulas are not used in benchmark scripts.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Documents''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.
